---
title: "Homework 6"
output: html_document
---

```{r echo=FALSE, message = FALSE}
#install.packages('dplyr')
library(dplyr)

shootings.2016 <- read.csv('data/shootings-2016.csv', stringsAsFactors = FALSE)

total.shooting <- nrow(shootings.2016)
total.kill <- shootings.2016 %>% summarise(total = sum(killed))

## most people got injured and killed.
table.city <- shootings.2016 %>% group_by(city) %>% summarise(total = sum(injured + killed))
most.affect.city <- shootings.2016 %>% group_by(city) %>% summarise(total = sum(injured + killed)) %>% filter(total == max(total)) %>% select(city)


# which day/month have the most people affected
table.date <- shootings.2016 %>% group_by(date) %>% summarise(total = sum(injured + killed))
day.most.shooting <- shootings.2016 %>% group_by(date) %>% summarise(total = sum(injured + killed)) %>% filter(total == max(total)) %>% select(date)
```
There are total of `r total.shooting` shooting occured in 2016. The total number of people killed is `r total.kill`. The city that got most death and injued are `r most.affect.city[1,]`. On day `r day.most.shooting` there are most people got killed or injured.

```{r echo=FALSE, message = FALSE}
#install.packages('knitr')
library(knitr)
library(dplyr)
top10 <- table.city %>% arrange(-total) %>% top_n(10)
kable(top10, caption = 'Total life Affect in Each City')
```

`The above table is the top 10 city with the most people's life affect, which is killed and injured`

```{r echo=FALSE, message = FALSE}
random.shooting <- sample_n(shootings.2016, 1)
date <- random.shooting$date
city <- random.shooting$city
state <- random.shooting$state
injured <- random.shooting$injured
killed <- random.shooting$killed
total <- killed + injured
```

For the incidence happed on `r date` at `r city`, `r state`, there are `r injured` people injured and `r killed` people got killed. There are total of `r total` people got affected in this incidence, not counting the family member got inloved. For more information on this incidence. Go to this [link](x)

```{r echo=FALSE, message = FALSE}
#install.packages('plotly')
library(plotly)
library(dplyr)

hover <- paste(shootings.2016$city, ', ', shootings.2016$state, '<br>', shootings.2016$date, '<br>', 'Injured', shootings.2016$injured, ', Killed', shootings.2016$killed)
plot_ly(type = 'scattergeo', lon = shootings.2016$lng, lat = shootings.2016$lat, text = hover, hoverinfo = 'text', mode = 'marker', opacity = 0.5, symbol = I('square')) %>% layout(geo = list(scope = 'usa'), title = 'Shooting in USA in 2016')

```

```{r echo=FALSE, message = FALSE}
library(plotly)
library(dplyr)

state.shooting <- shootings.2016 %>% group_by(state) %>% summarise(total = sum(injured + killed))
plot_ly(state.shooting, labels = ~state, values = ~total, type = 'pie', textposition = 'inside', textinfo = 'state', insidetextfont = list(color = '#FFFFFF'), opacity = 0.8, text = state, hoverinfo = 'text') %>% layout(title = '2016 Shooting Life Affect by State', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```
